\documentclass[10pt, conference, compsocconf]{IEEEtran}

\usepackage[bookmarks=true]{hyperref}
\usepackage{epsfig}
\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{epsf,picinpar}
\usepackage{varioref}
\usepackage{colortbl,multirow,hhline}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{colortbl,multirow,hhline}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[normalem]{ulem}
\usepackage{xcolor}
\usepackage{pifont}
\usepackage{xcolor,colortbl}
\usepackage{url}
\usepackage{balance}
\usepackage{graphicx, subfigure}
\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{listings}
\usepackage{framed}
\usepackage{morefloats}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{pdfpages}
\usepackage{fancybox}
\usepackage{amsmath}
\usepackage{flushend}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{adjustbox}
\usepackage[charter]{mathdesign}
\usepackage{eulervm}

\renewcommand{\ttdefault}{cmr}

\newcommand{\limit}[1]{\textcolor{red}{\ding{46}~Page limit:~#1}\\}
\newcommand{\todo}[1]{\textcolor{blue}{\ding{46}~#1}} 
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\etc}{etc.\xspace}
\newcommand{\etal}{\emph{et~al.}\xspace} 
    
\begin{document}

\title{
	{A Systematic Literature Review on Energy Efficiency in Robotics Software}
}

\author{
\IEEEauthorblockN{dr. Ivano Malavolta}
\IEEEauthorblockA{	
	Supervisor \\ 
	Vrije Universiteit Amsterdam
}

\vspace{5mm}

\IEEEauthorblockN{Stan Swanborn}
\IEEEauthorblockA{S2627602\\
s.o.swanborn@student.vu.nl}
}


\maketitle

\begin{abstract}
\noindent \textit{Context}. 
Nowadays, mobile robots are widely used in many applications. Non-mobile robots are widely used in industrial automation.
This literature study covers the field of research into the energy efficiency of robotics software.

\noindent \textit{Goal}. 
The goal of this literature study is to present a survey of existing research on energy efficiency in robotics software.

\noindent \textit{Method}. 
The method used is a rigorously designed literature study, spanning 17 primary studies. 
These primary studies are summarized, categorized, and analyzed in order to derive relevant patterns across the different studies.

\noindent \textit{Results}. 
The result is given in three parts, as answers to the three research questions. 
The results show that the field of study, while existing since before the change of the century, is still immature.
With attained interest over the last 5 to 10 years.
The results also gave rise to the motivation for the expansion of research into the energy impact of the robotics software itself.
This field of study is still very much in its infancy but proves essential in maximizing energy efficiency of robotic systems, 
as software is the main enabler of robotics, its energy consumption will directly inﬂuence the energy consumption level of the
entire system.

\noindent \textit{Conclusions}.
After reading this literature study, the reader will have gained insight in the state-of-the-art of analyzing and 
improving energy efficiency in robotics software. The reader will be able to judge the findings because of the analyzed publication trends
and will be able to judge if the findings are of use for their personal application using the explicate trade-off analysis.
\end{abstract}

\begin{IEEEkeywords}
Green Software, Robotics Software, Mobile Robots, Energy Efficiency, Systematic Literature Review, Systematic Literature Study
\end{IEEEkeywords}

\input{intro.tex}
\input{study_design.tex}
\input{results.tex} 
\input{discussion.tex}
\input{threats.tex}
\input{conclusion.tex} 

\bibliographystyle{IEEEtran}
\bibliography{references}

\input{appendix.tex}

\end{document}
